\begin{acknowledgments}
After five long and intense years, I am writing the last report during my time at Link\"oping University.
It has been five years of early mornings, late nights and and an uncountable amount of consumed cups of coffee.
Although is has not been a walk in the park, I have almost felt joy and inspiration every day, because I have been surrounded by amazing people.

First of all, I would like to thank Veoneer for given me the opportunity to perform my Master's thesis with them.
I would especially like to thank Patrik Leissner, my supervisor at Veoneer, for always being available to answer my questions and for his excellent driving skills when we recorded the data sets.
I would also like to thank everyone else at Veoneer who have helped me to complete this thesis.

Secondly, I would like to thank my supervisor at the university, Per Bostr\"om-Rost, for never being more than an email away.
I would also like to give credits to my examiner, Gustaf Hendeby.
He help me to point out the heading of this thesis during the ongoing work and played an important role for finalizing the structure of the thesis.
I would also like to mention Gustav Sandvik for helping me to proofread the thesis, and my opponent Johan Svensson for providing an interesting opposition session.

Lastly, I would like to thank everyone that I have meet during my time at Link\"oping University.
You have all helped me to become who I am today.
Thank you to all of my closest friends and especially to my family.
They have always supported me and brought so much joy and happiness into my life.
Thank you all!

  \addvspace{1em}
  \begin{flushright}
    \textit{%
      Linköping, June 2018\\
      Fredrik Nilsson%
    }
  \end{flushright}
\end{acknowledgments}
